Beam-Helicity and Charge Asymmetries \\ in the Bethe-Heitler and DVCS processes on \\ an Unpolarised Proton Target \underline{Paper Tag: PDVCS (v0.9)} \underline{Drafting Committee: DC90 (\today)}

### 2011-03-29 background_and_systematic.tex
Added the JHEP style

The data sample in the exclusive region contains events involving both production of real photons in which the proton remains intact and events involving the excitation of the target proton to a $\Delta^+$ resonant state. \blue{The} recoiling proton is not detected \blue{and the calorimeter resolution does not allow}, separation of the latter events from rest of the data sample.
No systematic uncertainty is assigned for the contribution from these events; they are treated as part of the signal. A Monte Carlo calculation based on the parameterisation \blue{from} Ref.~\cite{Bra76} is used to estimate the contribution to the event sample from resonant production in each kinematic bin. The results, denoted associated fraction and labelled ``Assoc. fraction'', are shown in the last row of each figure in the results section. The method used to perform \blue{this} estimation is described in detail in
Ref.~\cite{Air08}.

\begin{table}[H]
 \begin{center}
\resizebox{16cm}{!} {
 \begin{tabular}{|c|c|c|c|c|c|c|}
  \hline
 & $A$ $\pm$ $\delta_{stat.}$ $\pm$ $\delta_{syst.}$ & Background & Missing-Mass Shift & Detector Effects & & Total \\
  \hline
  \hline
  $A_{\textrm{LU,I}}^{\sin\phi}$ & -0.209  $\pm$  0.026  $\pm$   0.026 & 0.005 & 0.005 & 0.025 & & 0.026 \\
  \hline
  $A_{\textrm{LU,DVCS}}^{\sin\phi}$ & -0.015  $\pm$  0.026  $\pm$  0.008 & 0.004 & 0.007 & 0.001 & & 0.008 \\
  \hline
  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ & 0.005  $\pm$  0.025  $\pm$   0.005 & 0.005 & 0.001 & 0.002 & & 0.006 \\
  \hline
  \hline
  $A_{\textrm{C}}^{\cos(0\phi)}$ & -0.039 $\pm$  0.004 $\pm$  0.008 & 0.001 & 0.004 & 0.007 & & 0.008 \\
  \hline
  $A_{\textrm{C}}^{\cos\phi}$ & 0.032  $\pm$  0.006 $\pm$   0.003 & 0.002 & 0.001 & 0.002 & & 0.003 \\
  \hline
  $A_{\textrm{C}}^{\cos(2\phi)}$ & -0.007  $\pm$  0.006  $\pm$   0.002 & 0.001 & 0.001 & 0.001 & & 0.002 \\
  \hline
  $A_{\textrm{C}}^{\cos(3\phi)}$ & 0.009  $\pm$   0.006   $\pm$   0.001 & 0.000 & 0.001 & 0.001 & & 0.001 \\
  \hline
 \end{tabular}
}
  \caption{The contributions to the systematic uncertainty due to the
background correction, the time-dependent shifts of the missing-mass
distributions and detector effects for the 2006-2007 data to the total
systematic uncertainty. The total systematic uncertainties, shown in the
right-most column, are the individual contributions added in quadrature.}
  \label{table_systematic_contributions_0607}
\end{center}
\end{table}

>>>>

The data sample in the exclusive region contains events involving both
production of real photons in which the proton remains intact and
events involving the excitation of the target proton to a $\Delta^+$
resonant state. \blue{The} recoiling proton is not detected \blue{and
  the calorimeter resolution does not allow} separation of the latter events from rest of the data sample.
No systematic uncertainty is assigned for the contribution from these events; they are treated as part of the signal. A Monte Carlo calculation based on the parameterisation \blue{from} Ref.~\cite{Bra76} is used to estimate the contribution to the event sample from resonant production in each kinematic bin. The results, denoted associated fraction and labelled ``Assoc. fraction'', are shown in the last row of each figure in the results section. The method used to perform \blue{this} estimation is described in detail in
Ref.~\cite{Air08}.

\begin{table}
 \begin{center}
\resizebox{16cm}{!} {
 \begin{tabular}{|c|c|c|c|c|c|c|}
  \hline
 & $A$ $\pm$ $\delta_{stat.}$ $\pm$ $\delta_{syst.}$ & Background & Missing-Mass Shift & Detector Effects & & Total \\
  \hline
  \hline
  $A_{\textrm{LU,I}}^{\sin\phi}$ & -0.209  $\pm$  0.026  $\pm$   0.026 & 0.005 & 0.005 & 0.025 & & 0.026 \\
  \hline
  $A_{\textrm{LU,DVCS}}^{\sin\phi}$ & -0.015  $\pm$  0.026  $\pm$  0.008 & 0.004 & 0.007 & 0.001 & & 0.008 \\
  \hline
  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ & 0.005  $\pm$  0.025  $\pm$   0.005 & 0.005 & 0.001 & 0.002 & & 0.006 \\
  \hline
  \hline
  $A_{\textrm{C}}^{\cos(0\phi)}$ & -0.039 $\pm$  0.004 $\pm$  0.008 & 0.001 & 0.004 & 0.007 & & 0.008 \\
  \hline
  $A_{\textrm{C}}^{\cos\phi}$ & 0.032  $\pm$  0.006 $\pm$   0.003 & 0.002 & 0.001 & 0.002 & & 0.003 \\
  \hline
  $A_{\textrm{C}}^{\cos(2\phi)}$ & -0.007  $\pm$  0.006  $\pm$   0.002 & 0.001 & 0.001 & 0.001 & & 0.002 \\
  \hline
  $A_{\textrm{C}}^{\cos(3\phi)}$ & 0.009  $\pm$   0.006   $\pm$   0.001 & 0.000 & 0.001 & 0.001 & & 0.001 \\
  \hline
 \end{tabular}
}
  \caption{The contributions to the systematic uncertainty due to the
background correction, the time-dependent shifts of the missing-mass
distributions and detector effects for the 2006-2007 data to the total
systematic uncertainty. The total systematic uncertainties, shown in the
right-most column, are the individual contributions added in quadrature.}
  \label{table_systematic_contributions_0607}
\end{center}
\end{table}

### 2011-03-29 frame.tex
Added the JHEP style

\documentclass{elsart}
\usepackage[pdftex]{hyperref}
\usepackage{amstext,amsmath,amsfonts,amssymb}
\usepackage{bm}
\usepackage{lscape}
\usepackage{graphicx}
\usepackage{vruler}
\usepackage{color}
\usepackage{subfigure}
\usepackage{mathrsfs}
\usepackage{eufrak}
\usepackage{float}
%\usepackage{superscriptaddress}
\usepackage{rotating}
\textwidth 17.0cm
\oddsidemargin 0.0cm
\evensidemargin 0.0cm
\topmargin 0.5cm
% ===========================================================================

\begin{document}
\newcommand{\blue}[1]{{\color{blue}{#1}\color{black}}}
\newcommand{\red}[1]{{\color{red}{#1}\color{black}}}

\newcommand{\green}[1]{{\color{green}{#1}\color{black}}}
\newcommand{\yellow}[1]{{\color{yellow}{#1}\color{black}}}
\newcommand{\darkblue}[1]{{\color{darkblue}{#1}\color{black}}}
\newcommand{\darkgreen}[1]{{\color{darkgreen}{#1}\color{black}}}
\newcommand{\darkred}[1]{{\color{darkred}{#1}\color{black}}}
\newcommand{\lightred}[1]{{\color{lightred}{#1}\color{black}}}
\newcommand{\pink}[1]{{\color{pink}{#1}\color{black}}}
\newcommand{\gray}[1]{{\color{gray}{#1}\color{black}}}
\newcommand{\black}[1]{{\color{black}{#1}\color{black}}}
\newcommand{\magenta}[1]{\color{magenta}{#1}\color{black}}
\newcommand{\darkmag}[1]{\color{darkmag}{#1}\color{black}}

\def\CalT{\mathcal{T}}
\def\rmBH{\mathrm{BH}}
\def\rmDVCS{\mathrm{DVCS}}
\def\CalI{\mathcal{I}}
\def\rmunp{\mathrm{unp}}
\def\rmTP{\mathrm{TP}}
\def\rmRe{\mathrm{Re}}
\def\rmIm{\mathrm{Im}}

\def\xbj{x_{B}}
\def\qsr{Q^{2}}

\def\gpdH{\emph{H}}
\def\gpdE{\emph{E}}
\def\gpdHtil{\widetilde{H}}
\def\gpdEtil{\widetilde{E}}

\def\CalH{\mathcal{H}}
\def\CalE{\mathcal{E}}
\def\CalHtil{\widetilde{\mathcal{H}}}
\def\CalEtil{\widetilde{\mathcal{E}}}

\def\CalN{\mathcal{N}}
\def\CUU{\sigma_{U}}
\def\Lumi{\mathcal{L}\,}
\def\xx{\bm{x}}
\def\tt{\bm{\eta}}
\def\AC{A_C}
\def\AUT{A_{UT}}
\def\AUTDVCS{A_{UT,\rmDVCS}}
\def\AUTI{A_{UT,\CalI}}
\def\desy{{\sc desy}}

 \begin{frontmatter}

\title{
	Beam-Helicity and Charge Asymmetries \\
        in the Bethe-Heitler and DVCS processes on \\
        an Unpolarised Proton Target
  	\underline{Paper Tag: PDVCS (v0.9)}
        \underline{Drafting Committee: DC90 (\today)}
}

% List of Institute Addresses 
\collab{HERMES Collaboration}
\begin{abstract}
Beam-helicity and charge asymmetries in the hard exclusive leptoproduction of
real photons from an unpolarised proton target by a 27.6\,GeV lepton beam 
are extracted from the \blue{H{\sc ermes}} data set of 2006-2007 using a
missing-mass event selection technique. The beam-charge asymmetry amplitudes extracted from the new data set are statistically more precise than those extracted from \blue{the} earlier data set of 1996-2005 previously analysed in the same manner by the collaboration. Results from \blue{the two} data sets are found to be compatible with each other. Combined results from these data sets are extracted and \blue{represent} the statistically most precise asymmetry amplitude measurements available in the \blue{H{\sc ermes}} kinematic region.
\end{abstract}

\end{frontmatter}
% 
\setvruler[15pt][1][1][3][1][30pt][30pt][-42pt]
\include{theory}
\include{experiment_and_data}
\include{background_and_systematic}
\include{results}
\include{summary}
\include{append}
% this is a test comment to test the pull push mechanism
\bibliographystyle{ieeetr}
\bibliography{jburnsref}
\end{document}

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage{jheppub}
\pdfoutput=1
\toccontinuoustrue
\usepackage{lscape}
\usepackage{vruler}
\usepackage{subfigure}
\usepackage{appendix}

\newcommand{\blue}[1]{{\color{blue}{#1}\color{black}}}
\def\desy{{\sc desy}}

\begin{document}
\title{Beam-Helicity and Charge Asymmetries \\
        in the Bethe-Heitler and DVCS processes on \\
        an Unpolarised Proton Target
  	\underline{Paper Tag: PDVCS (v0.9)}
        \underline{Drafting Committee: DC90 (\today)}
}

% List of Institute Addresses 
\collaboration{The HERMES Collaboration}
\collaborationImg{\includegraphics{hermeslogo.pdf}}

\author[12]{A.~Airapetian}
\author[26]{N.~Akopov}
\author[5]{Z.~Akopov}
\author[6]{E.C.~Aschenauer}
\author[25]{W.~Augustyniak}
\author[26]{R.~Avakian}
\author[26]{A.~Avetissian}
\author[5]{E.~Avetisyan}
\author[15]{B.~Ball}
\author[18]{S.~Belostotski}
\author[10]{N.~Bianchi}
\author[17,24]{H.P.~Blok}
\author[6]{H.~B\"ottcher}
\author[5]{A.~Borissov}
\author[13]{J.~Bowles}
\author[12]{I.~Brodski}
\author[19]{V.~Bryzgalov}
\author[13]{J.~Burns}
\author[9]{M.~Capiluppi}
\author[10]{G.P.~Capitani}
\author[21]{E.~Cisbani}
\author[9]{G.~Ciullo}
\author[9]{M.~Contalbrigo}
\author[9]{P.F.~Dalpiaz}
\author[5]{W.~Deconinck}
\author[2]{R.~De~Leo}
\author[5,22]{L.~De~Nardo}
\author[10]{E.~De~Sanctis}
\author[8]{M.~Diefenthaler}
\author[10]{P.~Di~Nezza}
\author[17]{J.~Dreschler}
\author[12]{M.~D\"uren}
\author[12]{M.~Ehrenfried}
\author[26]{G.~Elbakian}
\author[4]{F.~Ellinghaus}
\author[6]{R.~Fabbri}
\author[10]{A.~Fantoni}
\author[22]{L.~Felawka}
\author[21]{S.~Frullani}
\author[6]{D.~Gabbert}
\author[19]{G.~Gapienko}
\author[19]{V.~Gapienko}
\author[21]{F.~Garibaldi}
\author[5,18,22]{G.~Gavrilov}
\author[26]{V.~Gharibyan}
\author[9]{F.~Giordano}
\author[15]{S.~Gliske}
\author[5]{M.~Golembiovskaya}
\author[10]{C.~Hadjidakis}
\author[5]{M.~Hartig}
\author[10]{D.~Hasch}
\author[23]{T.~Hasegawa}
\author[13]{G.~Hill}
\author[6]{A.~Hillenbrand}
\author[13]{M.~Hoek}
\author[5]{Y.~Holler}
\author[6]{I.~Hristova}
\author[23]{Y.~Imazu}
\author[19]{A.~Ivanilov}
\author[18]{A.~Izotov}
\author[1]{H.E.~Jackson}
\author[18]{A.~Jgoun}
\author[11]{H.S.~Jo}
\author[14]{S.~Joosten}
\author[13]{R.~Kaiser}
\author[26]{G.~Karyan}
\author[12]{T.~Keri}
\author[4]{E.~Kinney}
\author[18]{A.~Kisselev}
\author[23]{N.~Kobayashi}
\author[19]{V.~Korotkov}
\author[16]{V.~Kozlov}
\author[18]{P.~Kravchenko}
\author[7]{V.G.~Krivokhijine}
\author[2]{L.~Lagamba}
\author[14]{R.~Lamb}
\author[17]{L.~Lapik\'as}
\author[13]{I.~Lehmann}
\author[9]{P.~Lenisa}
\author[14]{L.A.~Linden-Levy}
\author[11]{A.~L\'opez~Ruiz}
\author[15]{W.~Lorenzon}
\author[5]{X.-G.~Lu}
\author[23]{X.-R.~Lu}
\author[3]{B.-Q.~Ma}
\author[13]{D.~Mahon}
\author[14]{N.C.R.~Makins}
\author[18]{S.I.~Manaenkov}
\author[21]{L.~Manfr\'e}
\author[3]{Y.~Mao}
\author[25]{B.~Marianski}
\author[4]{A.~Martinez de la Ossa}
\author[26]{H.~Marukyan}
\author[22]{C.A.~Miller}
\author[23]{Y.~Miyachi}
\author[26]{A.~Movsisyan}
\author[10]{V.~Muccifora}
\author[13]{M.~Murray}
\author[8]{A.~Mussgiller}
\author[2]{E.~Nappi}
\author[18]{Y.~Naryshkin}
\author[8]{A.~Nass}
\author[6]{M.~Negodaev}
\author[6]{W.-D.~Nowak}
\author[9]{L.L.~Pappalardo}
\author[12]{R.~Perez-Benito}
\author[8]{N.~Pickert}
\author[8]{M.~Raithel}
\author[1]{P.E.~Reimer}
\author[10]{A.R.~Reolon}
\author[6]{C.~Riedl}
\author[8]{K.~Rith}
\author[13]{G.~Rosner}
\author[5]{A.~Rostomyan}
\author[14]{J.~Rubin}
\author[11]{D.~Ryckbosch}
\author[19]{Y.~Salomatin}
\author[20]{F.~Sanftl}
\author[20]{A.~Sch\"afer}
\author[11]{G.~Schnell}
\author[5]{K.P.~Sch\"uler}
\author[13]{B.~Seitz}
\author[23]{T.-A.~Shibata}
\author[7]{V.~Shutov}
\author[9]{M.~Stancari}
\author[9]{M.~Statera}
\author[8]{E.~Steffens}
\author[17]{J.J.M.~Steijger}
\author[12]{H.~Stenzel}
\author[6]{J.~Stewart}
\author[8]{F.~Stinzing}
\author[26]{S.~Taroian}
\author[16]{A.~Terkulov}
\author[25]{A.~Trzcinski}
\author[11]{M.~Tytgat}
\author[11]{A.~Vandenbroucke}
\author[17]{P.B.~van~der~Nat}
\author[11]{Y.~Van~Haarlem}
\author[11]{C.~Van~Hulse}
\author[5]{M.~Varanda}
\author[18]{D.~Veretennikov}
\author[18]{V.~Vikhrov}
\author[2]{I.~Vilardi}
\author[8]{C.~Vogel}
\author[3]{S.~Wang}
\author[8]{S.~Yaschenko}
\author[3]{H.~Ye}
\author[5]{Z.~Ye}
\author[22]{S.~Yen}
\author[12]{W.~Yu}
\author[8]{D.~Zeiler}
\author[5]{B.~Zihlmann}
\author[25]{P.~Zupranski}

\affiliation[1]{Physics Division, Argonne National Laboratory, Argonne, Illinois 60439-4843, USA}
\affiliation[2]{Istituto Nazionale di Fisica Nucleare, Sezione di Bari, 70124 Bari, Italy}
\affiliation[3]{School of Physics, Peking University, Beijing 100871, China}
\affiliation[4]{Nuclear Physics Laboratory, University of Colorado, Boulder, Colorado 80309-0390, USA}
\affiliation[5]{DESY, 22603 Hamburg, Germany}
\affiliation[6]{DESY, 15738 Zeuthen, Germany}
\affiliation[7]{Joint Institute for Nuclear Research, 141980 Dubna, Russia}
\affiliation[8]{Physikalisches Institut, Universit\"at Erlangen-N\"urnberg, 91058 Erlangen, Germany}
\affiliation[9]{Istituto Nazionale di Fisica Nucleare, Sezione di Ferrara and Dipartimento di Fisica, Universit\`a di Ferrara, 44100 Ferrara, Italy}
\affiliation[10]{Istituto Nazionale di Fisica Nucleare, Laboratori Nazionali di Frascati, 00044 Frascati, Italy}
\affiliation[11]{Department of Subatomic and Radiation Physics, University of Gent, 9000 Gent, Belgium}
\affiliation[12]{Physikalisches Institut, Universit\"at Gie{\ss}en, 35392 Gie{\ss}en, Germany}
\affiliation[13]{SUPA, School of Physics and Astronomy, University of Glasgow, Glasgow G12 8QQ, United Kingdom}
\affiliation[14]{Department of Physics, University of Illinois, Urbana, Illinois 61801-3080, USA}
\affiliation[15]{Randall Laboratory of Physics, University of Michigan, Ann Arbor, Michigan 48109-1040, USA }
\affiliation[16]{Lebedev Physical Institute, 117924 Moscow, Russia}
\affiliation[17]{National Institute for Subatomic Physics (Nikhef), 1009 DB Amsterdam, The Netherlands}
\affiliation[18]{Petersburg Nuclear Physics Institute, Gatchina, Leningrad region, 188300 Russia}
\affiliation[19]{Institute for High Energy Physics, Protvino, Moscow region, 142281 Russia}
\affiliation[20]{Institut f\"ur Theoretische Physik, Universit\"at Regensburg, 93040 Regensburg, Germany}
\affiliation[21]{Istituto Nazionale di Fisica Nucleare, Sezione Roma 1, Gruppo Sanit\`a and Physics Laboratory, Istituto Superiore di Sanit\`a, 00161 Roma, Italy}
\affiliation[22]{TRIUMF, Vancouver, British Columbia V6T 2A3, Canada}
\affiliation[23]{Department of Physics, Tokyo Institute of Technology, Tokyo 152, Japan}
\affiliation[24]{Department of Physics and Astronomy, Vrije Universiteit, 1081 HV Amsterdam, The Netherlands}
\affiliation[25]{Andrzej Soltan Institute for Nuclear Studies, 00-689 Warsaw, Poland}
\affiliation[26]{Yerevan Physics Institute, 375036 Yerevan, Armenia}

\abstract{
Beam-helicity and charge asymmetries in the hard exclusive leptoproduction of real photons from an unpolarised proton target by a 27.6\,GeV lepton beam 
are extracted from the \blue{H{\sc ermes}} data set of 2006-2007 using a missing-mass event selection technique. The beam-charge asymmetry amplitudes extracted from the new data set are statistically more precise than those extracted from \blue{the} earlier data set of 1996-2005 previously analysed in the same manner by the collaboration. Results from \blue{the two} data sets are found to be compatible with each other. Combined results from these data sets are extracted and \blue{represent} the statistically most precise asymmetry amplitude measurements available in the \blue{H{\sc ermes}} kinematic region.
}
\keywords{lepton-nucleon scattering}

\setvruler[15pt][1][1][3][1][30pt][30pt][-42pt]
\maketitle

\include{theory}
\include{experiment_and_data}
\include{background_and_systematic}
\include{results}
\include{summary}
\include{append}
\bibliographystyle{natbib}
\bibliography{jburnsref}
\end{document}

### 2011-03-29 summary.tex
Added the JHEP style

>>>>

\acknowledgments
We gratefully acknowledge the \desy\ management for its support and the staff
at \desy\ and the collaborating institutions for their significant effort.
This work was supported by 
the Ministry of Economy and the Ministry of Education and Science of Armenia;
the FWO-Flanders and IWT, Belgium;
the Natural Sciences and Engineering Research Council of Canada;
the National Natural Science Foundation of China;
the Alexander von Humboldt Stiftung,
the German Bundesministerium f\"ur Bildung und Forschung (BMBF), and
the Deutsche Forschungsgemeinschaft (DFG);
the Italian Istituto Nazionale di Fisica Nucleare (INFN);
the MEXT, JSPS, and G-COE of Japan;
the Dutch Foundation for Fundamenteel Onderzoek der Materie (FOM);
the Russian Academy of Science and the Russian Federal Agency for 
Science and Innovations;
the U.K.~Engineering and Physical Sciences Research Council, 
the Science and Technology Facilities Council,
and the Scottish Universities Physics Alliance;
the U.S.~Department of Energy (DOE) and the National Science Foundation (NSF);
and the European Community Research Infrastructure Integrating Activity
under the FP7 "Study of strongly interacting matter (HadronPhysics2, Grant
Agreement number 227431)".
